The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-11-01 ms.Rmd

A lack of sharing reduces the capacity for innovation and validation in SDM, as well as its capacity to be a "self-correcting process" [@roysoc_report].
For example, a fundamental dispute over the ability of SDM to detect environmental associations [@Beale2008, @Araujo2009, @Beale2009] was left unresolved as only the original publication shared their analytical code [@Beale2008].
Without the resources being made open the critical differences in these analytical steps are assumed rather than proven.

>>>>

A lack of sharing reduces the capacity for innovation and validation in SDM, as well as its capacity to be a "self-correcting process" [@Boulton2012].
For example, a fundamental dispute over the ability of SDM to detect environmental associations [@Beale2008, @Araujo2009, @Beale2009] was left unresolved as only the original publication shared their analytical code [@Beale2008].
Without the resources being made open the critical differences in these analytical steps are assumed rather than proven.
